Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-13 paper.tex
Move todo item to #39
Remove list of todos and add line numbers
Minor fix in abstract

% Abstract (Less than 200 words)
\abstract{The performance and wake characteristics of cross-flow (vertical axis)
    turbines depend on many parameters: solidity, blade profile, blade pitch, number
    of blades, strut drag, operational parameters such as tip speed ratio---and
    Reynolds number. Tolerable mismatch between physical model Reynolds number and
    full-scale Reynolds number was investigated from both the perspective of
    predicting full scale performance and flow dynamics, as well as numerical model
    validation. Experiments were performed with a large laboratory-scale cross-flow
    turbine of to investigate Reynolds number dependence of performance and wake
    transport characteristics, and to determine what an acceptable Reynolds number
    mismatch is for scaled physical model tests of cross-flow turbines. It was
    demonstrated that the performance of the cross-flow turbine becomes essentially
    $Re$-independent at a Reynolds number based on turbine diameter of $Re_D \approx
    10^6$, or an approximate Reynolds number based on blade chord of $Re_c \approx 2
    \times 10^5$. A simple model that calculates peak torque coefficient from static
    foil data and cross-flow turbine kinematics was shown to be a reasonable
    estimator for predicting Reynolds number dependence of an actual cross-flow
    turbine operating under dynamic conditions.}

@@

\begin{document}
%\linenumbers
\listoftodos

@@

\todo[inline]{Issues such as blade termination/strength of tip vortices?}

>>>>

% Abstract (Less than 200 words)
\abstract{The performance and wake characteristics of cross-flow (vertical axis)
    turbines depend on many parameters: solidity, blade profile, blade pitch, number
    of blades, strut drag, operational parameters such as tip speed ratio---and
    Reynolds number. Tolerable mismatch between physical model Reynolds number and
    full-scale Reynolds number was investigated from both the perspective of
    predicting full scale performance and flow dynamics, as well as numerical model
    validation. Experiments were performed with a large laboratory-scale high
    solidity cross-flow turbine to investigate Reynolds number dependence of
    performance and wake transport characteristics, and to determine what an
    acceptable Reynolds number mismatch is for scaled physical model tests of
    cross-flow turbines. It was demonstrated that the performance of the cross-flow
    turbine becomes essentially $Re$-independent at a Reynolds number based on
    turbine diameter of $Re_D \approx 10^6$, or an approximate Reynolds number based
    on blade chord of $Re_c \approx 2 \times 10^5$. A simple model that calculates
    peak torque coefficient from static foil data and cross-flow turbine kinematics
    was shown to be a reasonable estimator for predicting Reynolds number dependence
    of an actual cross-flow turbine operating under dynamic conditions.}

@@

\begin{document}
\linenumbers

@@
